---
output: github_document
---

## Preamble

The {orit}-package in intended to be helpful when parsing messages from "Hafriti". The aim is that all variables are returned as correct types (integer, numeric, character, date, time, datetime, etc.).

## Test run

Here we use subsample of data from the Postgres database with up to 1000 records of each "message type" from research vessels Árni and Bjarni.

### Needed libraries

```{r}
#| message: false
#| warning: false
library(tidyverse)
library(orit)
```

### Data preparations

```{r}
# The subsample data, use shorter name for "nmea_message"
pg <- postgres_test_data |> rename(m = nmea_message)
# Get the types, but excludes types not yet dealt with
TYPES <-
  pg |>
  filter(!type %in% c("NO IDEA")) |>
  pull(type) |> unique() |> sort()
TYPES
```

### Data prior to parsing

The following is a peek at the first two records from each vessel for each type:


```{r}
pg |> 
  group_by(type, skip) |> 
  slice(1:2) |> 
  ungroup() |> 
  select(skip, type, m) |> 
  as.data.frame() |> 
  print()
```


### Parse each message type and print out some results

```{r}
res <- list()
for(t in 1:length(TYPES)) {
  print(TYPES[t])
  res[[t]] <-
    hr_message_parse(pg, TYPES[t])
  res[[t]] |> glimpse()
}
names(res) <- TYPES
```

## Still known problems

### type GLL

* Seems like Bjarni does not have variable "faa_mode" (the last field prior to "check"):

```{r}
pg |> 
  filter(type == "GLL") |> 
  group_by(skip) |> 
  slice(1:2) |> 
  ungroup() |> 
  select(skip, m)
```

### type HBT

THIS IS SOLVED

Unknown format:

```{r}
pg |> 
  filter(type == "HBT") |> 
  group_by(skip) |> 
  slice(1:2) |> 
  ungroup() |> 
  select(skip, m)
```

### type MSD

THIS IS SOLVED

Unknown format:

```{r}
pg |> 
  filter(type == "MSD") |> 
  group_by(skip) |> 
  slice(1:2) |> 
  ungroup() |> 
  select(skip, m)
```

### type SM2

THIS IS SOLVED

EXCEPT: THE TIME - need origin

Unknown format:

```{r}
pg |> 
  filter(type == "SM2") |> 
  group_by(skip) |> 
  slice(1:2) |> 
  ungroup() |> 
  select(skip, m)
```

### type XDR

Get message: NAs introduced by coercion

```{r}
pg |> 
  filter(type == "XDR") |> 
  group_by(skip) |> 
  slice(1:2) |> 
  ungroup() |> 
  select(skip, m)
```

### NO IDEA

```{r}
pg |> 
  filter(type == "NO IDEA") |> 
  count(message_type)
```

